Preprocess

### 2025-10-12 src/data.Rmd
Include gpt5 data

@@

@@

```{r}
write_csv(out, "../data/healsl_rd1to2_cod_v1.csv")
```

>>>>

    model_gpt5 =
            "../tmp/healsl_rd1to2_rapid_gpt5_v1.csv",
            col_select = c("rowid", "cause1_icd10", "round")
            round = as.integer(substr(round, 3, 3))
        ) %>% rename(gpt5_icd10 = cause1_icd10),

@@

### ChatGPT-5 Counts

Check ChatGPT-5 Counts:

# Get gpt5 coded records
out_cgpt5 <- out_coded %>% filter(
    !is.na(gpt5_icd10) & !is.null(gpt5_icd10)
)
out_cgpt5_agree <- out_coded_agree %>% filter(
    !is.na(gpt5_icd10) & !is.null(gpt5_icd10)
)
out_cgpt5_cghr10 <- out_coded_cghr10 %>% filter(
    !is.na(gpt5_icd10) & !is.null(gpt5_icd10)
)
out_cgpt5_cghr10_agree <- out_coded_cghr10_agree %>% filter(
    !is.na(gpt5_icd10) & !is.null(gpt5_icd10)
)

# Get gpt5 coded records converted to cghr10
out_cgpt5_xcghr10 <- out_cgpt5 %>% filter(
    !is.na(gpt5_cghr10) & !is.null(gpt5_cghr10)
)
out_cgpt5_xcghr10_agree <- out_cgpt5_agree %>% filter(
    !is.na(gpt5_cghr10) & !is.null(gpt5_cghr10)
)
out_cgpt5_xcghr10_cghr10 <- out_cgpt5_cghr10 %>% filter(
    !is.na(gpt5_cghr10) & !is.null(gpt5_cghr10)
)
out_cgpt5_xcghr10_cghr10_agree <- out_cgpt5_cghr10_agree %>% filter(
    !is.na(gpt5_cghr10) & !is.null(gpt5_cghr10)
)

# Print results
cat(paste0(
    "ICD-10 Output\n-------------",
    "\nChatGPT-5 ICD-10 Coded (Phy. ICD-10 Coded): ", out_cgpt5 %>% nrow,
    "\nChatGPT-5 ICD-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt5_agree %>% nrow,
    "\nChatGPT-5 ICD-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt5_cghr10 %>% nrow,
    "\nChatGPT-5 ICD-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt5_cghr10_agree %>% nrow,
    "\n\nAfter Conversion to CGHR-10\n---------------------------",
    "\nChatGPT-5 CGHR-10 Coded (Phy. ICD-10 Coded): ", out_cgpt5_xcghr10 %>% nrow,
    "\nChatGPT-5 CGHR-10 Coded (Agree, Phy. ICD-10 Coded): ", out_cgpt5_xcghr10_agree %>% nrow,
    "\nChatGPT-5 CGHR-10 Coded (Phy. CGHR-10 Coded): ", out_cgpt5_xcghr10_cghr10 %>% nrow,
    "\nChatGPT-5 CGHR-10 Coded (Agree, Phy. CGHR-10 Coded): ", out_cgpt5_xcghr10_cghr10_agree %>% nrow
))
```

@@

```{r}
write_csv(out, "../data/healsl_rd1to2_cod_v2.csv")
```
